Notes

### 2024-11-21 article.qmd
doc: update

However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind speed derived from solar wind propagation models. Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location. This model, which utilizes the BATSRUS MHD solver[@tothAdaptiveNumericalAlgorithms2012], simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study. The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model. The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.

>>>>

However, since Juno does not provide direct plasma measurements, we will estimate the spatial scale (thickness) of discontinuities using solar wind plasma state data derived from solar wind propagation models. Specifically, we will employ the Two-Dimensional Outer Heliosphere Solar Wind Modeling (MSWIM2D) [@keeblerMSWIM2DTwodimensionalOuter2022] to determine the ion bulk velocity ($v$) and plasma density ($n$) at Juno’s location. This model, which utilizes the BATSRUS MHD solver[@tothAdaptiveNumericalAlgorithms2012], simulates the propagation of solar wind from 1 to 75 astronomical units (AU) in the ecliptic plane, effectively covering the region pertinent to our study. The MSWIM2D model provides output data with an hourly time resolution as shown in @fig-model. The comparison of magnetic field magnitudes from MSWIM2D with those measured by Juno, after averaging to the same time resolution, reveals a strong correlation, confirming the model’s reliability.

### 2024-11-21 notes.qmd
doc: update

@@

Sadly, JUNO does not provide plasma data during the cruise phase, so to estimate the plasma state we will use MHD model.

We are using [Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/), which models the solar wind propagation in 2D using the BATSRUS MHD solver. @keeblerMSWIM2DTwodimensionalOuter2022

@@

-   Analysis
    -   [ ] Re-calculate the occurrence rate of IDs
    -   [x] Distribution of $δB/B$ over radius (related to the alfvenicity, identification standard about neighboring fluctuations)
    -   [x] $\theta_{n,v}$ distribution
    -   [ ] Correlation between plasma beta and thickness / current density

    -   [ ] Check Datagap
    -   [ ] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] Distribution of \|B\| over radius
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [ ] Wind data
    -   [ ] Add error bar
    -   [ ] Validate the effects of calibrate candidate duration

    -   ~~Contribution of discontinuities to the power spectrum~~
    -   ~~Validate model density with `Voyager`~~
-   Identifaction
    -   [ ] Ensemble forest?
    -   [ ] Smoothing is important?
    -   [ ] Check change point algorithm
-   Visualize data gaps
-   Features
    -   [ ] Thickness in N direction
    -   [ ] Use high resolution data for feature extraction
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation

>>>>

Sadly, JUNO does not provide plasma data during the cruise phase, so we use MHD model to estimate the plasma state.

[Michigan Solar WInd Model 2D (MSWIM2D)](http://csem.engin.umich.edu/MSWIM2D/) models the solar wind propagation in 2D using the BATSRUS MHD solver [@keeblerMSWIM2DTwodimensionalOuter2022].

@@

@@

-   Analysis
    -   [ ] Texts about waiting time distribution
    -   [ ] Re-calculate the occurrence rate of IDs
    -   [x] Distribution of $δB/B$ over radius (related to the alfvenicity, identification standard about neighboring fluctuations)
    -   [x] $\theta_{n,v}$ distribution
    -   [ ] Correlation between plasma beta and thickness / current density

    -   [ ] Check datagap and visualize the data gap
    -   [x] Check `ARTEMIS-B` data in different states (solar wind, magnetosheath, magnetotail, moon wake)
    -   [ ] JUNO from 2012-09\~2012-10 lack of IDS and extreme large thickness
    -   [x] Wind data

    -   ~~Validate the effects of calibrate candidate duration~~
    -   ~~Contribution of discontinuities to the power spectrum~~
    -   ~~Validate model density with `Voyager`~~
-   Identifaction
    -   [ ] Ensemble forest?
    -   [x] Smoothing is important?
    -   [ ] Check change point algorithm
-   Compare with other methods of identifying IDs
    -   [ ] Verify with other methods of identifying IDs
-   [x] Incorporate solar wind propagation model
    -   [x] Verify with solar wind propagation model
        -   [x] Coordinate transformation
